### 2018-06-03 Sections/optimising_the_world.tex
Touch up

\begin{figure}[!htb]
	\includegraphics[width=0.4\textwidth]{traffic_optimisation}
	\caption{Simple road network, where vertices represent intersections and edges represent roads. Edge weights indicate their associated travel time. The goal is for Alice and Bob to both drive home optimally, i.e minimising net commute time. Let us assume that the intersections do not delay single cars, but if they become congested (i.e more than one car simultaneously) they induce a time delay of 1 on all drivers present at the intersection. If Bob were to stay at work, and only Alice was attempting to drive home, her optimal route would be \mbox{$A\to D\to F$}, with a commute time of 2. Conversely, if Alice stayed at work and Bob was driving home, his optimal route would be \mbox{$B\to D\to G$}, also with a commute time of 2. However, if both Alice and Bob were driving home at the same time there would be congestion at intersection $D$, and their combined travel time would be 6, not the intended 4. Thus, by optimising their routes independently of one another their competition for intersection $D$ would penalise both of them by 1. On the other hand, a global optimisation would show that a more optimal routing would be for Alice to take \mbox{$A\to C\to F$} (time 2.5), with Bob remaining on \mbox{$B\to D\to G$} (time 2). This would penalise Alice by only 0.5 for taking the longer road, but both Alice and Bob would no longer be penalised at the congested intersection, reducing their collective transit time to 4.5, a saving of 1.5. Note that Alice and Bob are not only better off collectively (i.e their joint travel time), but also individually. That is, Alice making the sacrifice of taking the longer route home actually benefits her individually, with an individual saving of 0.5.}\label{fig:traffic_opt}
\end{figure}

@@

An intuitive example of a problem taken from a far harder complexity class than \textbf{NP}-complete, that can be approximately optimised using the Grover approach is the game of chess\index{Chess}. Generalisation of the rules of chess to an \mbox{$n\times n$} board yields a game proven to reside in \textbf{EXP}-complete\index{\textbf{EXP}-complete} -- an \textit{extremely} hard class.

>>>>

\begin{figure}[!htb]
	\includegraphics[width=0.4\textwidth]{traffic_optimisation}
	\caption{Simple road network, where vertices represent intersections and edges represent roads. Edge weights indicate their associated travel time. The goal is for Alice and Bob to both drive home optimally, i.e minimising net commute time. Let us assume that the intersections do not delay single cars, but if they become congested (i.e more than one car simultaneously) they induce a time delay of 1 on all drivers present at the intersection. If Bob were to stay at work, and only Alice was attempting to drive home, her optimal route would be \mbox{$A\to D\to F$}, with a commute time of 2. Conversely, if Alice stayed at work and Bob was driving home, his optimal route would be \mbox{$B\to D\to G$}, also with a commute time of 2. However, if both Alice and Bob were driving home at the same time there would be congestion at intersection $D$, and their combined travel time would be 6, not the intended 4. Thus, by optimising their routes independently of one another their competition for intersection $D$ would penalise both of them by 1. On the other hand, a global optimisation would show that a more optimal routing would be for Alice to take \mbox{$A\to C\to F$} (time 2.5), with Bob remaining on \mbox{$B\to D\to G$} (time 2). This would penalise Alice by only 0.5 for taking the longer road, but both Alice and Bob would no longer be penalised at the congested intersection, reducing their collective transit time to 4.5, a saving of 1.5. Note that Alice and Bob are not only better off collectively (i.e their joint travel time), but also individually. That is, Alice making the sacrifice of taking the longer route home actually benefits her individually, with an individual saving of 0.5. In this trivial example there is only one point of conflict in the network. In general, as the number of users scales up, the distinct ways in which combinations of conflicts could emerge grows exponentially.}\label{fig:traffic_opt}
\end{figure}

@@

An intuitive example of a problem taken from a far harder complexity class than \textbf{NP}-complete, that can be approximately optimised using the Grover approach is the game of chess\index{Chess}. Generalisation of the rules of chess to an \mbox{$n\times n$} board yields a game proven to reside in \textbf{EXP}-complete\index{\textbf{EXP}-complete} -- the class of all problems requiring exponential runtime on a classical computer.
